Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
pp-check

colSums(is.na(model_data))

model_10 <- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + percent_white,
  data = model_data, family = gaussian, chains = 4, iter = 1000
)
```
```{r}
head(data.frame(summary(model_10)),-2)
```

@@

```{r}
set.seed(454)
#Neg Rate
model_14 <- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + negative_rate,
  data = mod_data, family = gaussian, chains = 4, iter = 1000
)
```

@@

@@

```{r}
model_15<-stan_glmer(
  ChinaVirusInterest ~ (Day|State) + negative_rate, 
  data=mod_data, family=gaussian, chains =4, iter = 5000
)
```

```{r}
head(data.frame(summary(model_15)),-2)
```

```{r}
# Store the chains
model_15_df <- as.array(model_15) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_15_df <- model_15_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_15_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

@@

@@

```{r}
# Pct black, Neg Rate: Random effects
model_17<-stan_glmer(
  ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
  data = mod_data, family = gaussian, chains = 4, iter = 2*5000

)
```

```{r}

head(data.frame(summary(model_5),-2))

head(data.frame(summary(model_17)),-2)
```

```{r}
model_17_df <- as.array(model_17) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_17_df <- model_17_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_17_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

>>>>

colSums(is.na(model_data))
```
```{r}
model_10 <- stan_glmer(
  ChinaVirusInterest ~ Day + (1 | State) + percent_white,
  data = model_data, family = gaussian, chains = 4, iter = 1000
)
```
```{r}
head(data.frame(summary(model_10)),-2)
```

@@

Model 14
```{r}
set.seed(454)
#Neg Rate
model_14 <- stan_glmer(
  ChinaVirusInterest ~ (1 | State) + negative_rate,
  data = mod_data, family = gaussian, chains = 4, iter = 1000
)
```

@@

Checking Model 14
```{r}
mcmc_trace(model_14)
mcmc_dens(model_14)
```
```{r}
pp_check(model_14, nreps=50)
```

@@

```{r}
set.seed(454)
my_data <- data.frame(negative_rate = .9, State = "IL", percent_black = .12)

 # Simulate a set of predictions for each case in newdata
my_prediction <- posterior_predict(
   model_14,
   newdata = my_data)

my_prediction <- data.frame(y_new = my_prediction[,1])

ggplot(my_prediction, aes(x = y_new)) +
  geom_density()

summary(my_prediction)
```

```{r}
# model_15<-stan_glmer(
#   ChinaVirusInterest ~ (Day|State) + negative_rate, 
#   data=mod_data, family=gaussian, chains =4, iter = 5000
# )
```

```{r}
# head(data.frame(summary(model_15)),-2)
```

```{r}
# # Store the chains
# model_15_df <- as.array(model_15) %>% 
#   melt %>% 
#   pivot_wider(names_from = parameters, values_from = value)
# 
# # Wrangle the chains
# # Note the need for `...` around the sigma_sq_b
# model_15_df <- model_15_df %>% 
#   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
#   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
# 
# ggplot(model_15_df, aes(x = correlation)) + 
#   geom_density(alpha = 0.5)
```

@@

```{r}
mcmc_trace(model_16)
mcmc_dens(model_16)
```

```{r}
pp_check(model_16, iter=50)
```

@@

```{r}
set.seed(454)
my_data <- data.frame(negative_rate = .9, State = "IL", percent_black = .12)

 # Simulate a set of predictions for each case in newdata
my_prediction <- posterior_predict(
   model_16,
   newdata = my_data)

my_prediction <- data.frame(y_new = my_prediction[,1])

ggplot(my_prediction, aes(x = y_new)) +
  geom_density()

summary(my_prediction)
```

```{r}
# # Pct black, Neg Rate: Random effects
# model_17<-stan_glmer(
#   ChinaVirusInterest~ (Day|State) + percent_black + negative_rate, 
#   data = mod_data, family = gaussian, chains = 4, iter = 2*5000
# 
# )
```

```{r}
# head(data.frame(summary(model_17)),-2)
```

```{r}
# model_17_df <- as.array(model_17) %>% 
#   melt %>% 
#   pivot_wider(names_from = parameters, values_from = value)
# 
# # Wrangle the chains
# # Note the need for `...` around the sigma_sq_b
# model_17_df <- model_17_df %>% 
#   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
#   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
# 
# ggplot(model_17_df, aes(x = correlation)) + 
#   geom_density(alpha = 0.5)
```
